### 2022-11-21 ms.rmd
Ditch contrasts
extracting posteriors

  } else{
  model1.2 <- readRDS("./output/models/lnRRQ10_1.2")
}

@@

summary(glht(model1.2, linfct=rbind(c(-1,0,1,0,0,0,0), c(1,0,1,-1,0,1,0)), test=adjusted("none")))

>>>>

  } else{
  model1.2 <- readRDS("./output/models/lnRRQ10_1.2")
  model1.2_bayes <- readRDS("./output/models/lnRRQ10_1.2_bayes")
}

@@

## Contrasts
posteriors_1.2 <- posterior_samples(model1.2_bayes, pars = "^b")
f_acute  <- posteriors_1.2[,"b_Intercept"] 
f_acclim <- posteriors_1.2[,"b_Intercept"] + posteriors_1.2[,"b_typeacclim"]
